---
title: "p8105_hw5_jy3270"
author: "Jingya Yu"
date: "2022-11-16"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


## Problem 1(provided by professor)

The code chunk below imports the data in individual spreadsheets contained in `./data/zip_data/`. To do this, I create a dataframe that includes the list of all files in that directory and the complete path to each file. As a next step, I `map` over paths and import data using the `read_csv` function. Finally, I `unnest` the result of `map`.

```{r}
full_df = 
  tibble(
    files = list.files("data/zip_data/"),
    path = str_c("data/zip_data/", files)
  ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest()
```

The result of the previous code chunk isn't tidy -- data are wide rather than long, and some important variables are included as parts of others. The code chunk below tides the data using string manipulations on the file, converting from wide to long, and selecting relevant variables. 

```{r}
tidy_df = 
  full_df %>% 
  mutate(
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>% 
  select(group, subj = files, week, outcome)
```

Finally, the code chunk below creates a plot showing individual data, faceted by group. 

```{r}
tidy_df %>% 
  ggplot(aes(x = week, y = outcome, group = subj, color = group)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group)
```

This plot suggests high within-subject correlation -- subjects who start above average end up above average, and those that start below average end up below average. Subjects in the control group generally don't change over time, but those in the experiment group increase their outcome in a roughly linear way. 

## Problem 2
```{r}
homicide <- read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv")
head(homicide)
```
The dataset has `r nrow(homicide)` observations and `r ncol(homicide)` variables. Each observation is a homicide case, along with the case number, reported date, victim's first and last names, race, age, and sex, the location of the case (city, state, latitude, and longitude), and the disposition of the case.  

- create a city-state variable
```{r}
homicide = homicide %>%
  mutate(city_state = str_c(city, state, sep = ", "))
head(homicide)
```

Summarize within cities to get the total count of homicides and the total count of unsolved homicides.
```{r}
summary = homicide %>%
  group_by(city_state) %>%
  summarize(total_count = n(),
            unsolved_cases = sum(disposition %in% c("Closed without arrest", "Open/No arrest"))) %>% 
 filter(city_state != "Tulsa, AL") 
summary
```

For the city of Baltimore, MD. We use the prop.test function to estimate the proportion of homicides that are unsolved
```{r}
baltimore = summary %>%
  filter(city_state == "Baltimore, MD") 
  
baltimore_proptest = prop.test(baltimore$unsolved_cases, baltimore$total_count) %>% 
  broom::tidy() %>%
  select(estimate, conf.low, conf.high) 
baltimore_proptest
```
For all the cities
```{r}
city_proptests = 
  purrr::map2_df(.x = summary$unsolved_cases,
            .y = summary$total_count,
            ~broom::tidy(prop.test(.x, .y))) %>%
  select(estimate, conf.low, conf.high) %>%
  mutate(city_state = summary$city_state) %>%
  relocate(city_state)
city_proptests
```

Create a plot that shows the estimates and CIs for each city 
```{r}
ggplot(city_proptests, 
       aes(x = estimate, y = fct_reorder(city_state, estimate, .desc=F))) +
  geom_col() +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high)) + 
  labs(title = "Estimated proportion and CI of unsolved homicides by city",
       x = "proportion of unsolved murders", y = "city_state")
```

## Problem 3
- set the variable
```{r}
#devtools::install_github("simsem/simsem/simsem")
n = 30
sigma = 5
```

generate 5000 datasets from the normal distribution. For each dataset, save the estimate $\hat \mu$ and the p-value arising from a test of H: $\mu = 0$ using $\alpha = 0.05$. 
```{r}
mu = 0
sim_results_mu_0 = 
  expand_grid(mu = mu, 
              iter = 1:5000) %>%
  mutate(sample = map(.x = mu, ~rnorm(n, .x, sigma))) %>%
  mutate(estimate_df = map(.x = sample, 
                           ~broom::tidy(t.test(.x, 
                                               alternative = "two.sided",
                                               conf.level = 0.95)))) %>%
  unnest(estimate_df) %>%
  select(mu, iter, estimate, p.value)
sim_results_mu_0
```

